Look, we can do something

### 2024-11-11 paper.tex
This is the end (no)

@@

Flaws of this parameter include:
\begin{itemize}
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\end{itemize}

The first flaw can be dealt with by replacing the Euclidean distance in
\cref{eq:intro} with the length of the shortest path between points which does
not cross the pore's boundary. This, however, can increase computational time
significantly.

>>>>

The parameter \cref{eq:awesomeness} is scale- and rotation-invariant. The
algorithm presented in this paper changes the parameter by about 10\% when
rotating an image of a pore or scaling it by a factor $0.5-2$. This inaccuracy
is OK for assessing quality of pore clusterization, as can be seen in the next
section.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/rotation-resize.png}
  \caption[]{\highlight{Awesomeness} parameter for the same image under rotation
  (red X marks) and resize (blue dot marks) transforms.}
  \label{fig:rotation-resize}
\end{figure}

@@

Flaws of this parameter include:
\begin{itemize}
\item Sometimes the shortest path between two points on a pore's boundary either:
  \begin{itemize}
  \item has more than two common points with the boundary;
  \item lies entirely in the pore's exterior (with exception of end points).
  \end{itemize}
  In this case the two points definitely cannot form a bottleneck.
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\end{itemize}

The first flaw can be dealt with by replacing the Euclidean distance $\rho_{AB}$
in \cref{eq:intro} with the length $d_{AB}$ of the shortest path between points
which does not cross the pore's boundary. Although the resulting algorithm will
have the same $O(n^2)$ complexity, doing so can increase computational time
significantly. We call the parameter $P'$ with $d_{AB}$ in the place of
$\rho_{AB}$ ``improved awesomeness''.

We present an opensource solution for calculating \highlight{awesomeness} and
improved \highlight{awesomeness}. \highlight{E-mail us and buy us coffee so we
  can send this super program to you, no matter where you live! Hurry, this is a
limited offer!} An average time for calculating \highlight{awesomeness} is 1
second for a $1000 \times 1000$ png image and is $1-60$ seconds for calculating
improved \highlight{awesomeness}.
